Survey Results from: Meta-analytic approaches and new effect sizes to account for heterogeneous effects in comparative physiology

### 2021-07-14 R/survey_data_results.Rmd
Adding some more finesclae resolution to quetsions

@@

>>>>

How do the two categorisations (meta-analysis and weighting) combine?

```{r}
dat %>% 
  ggplot() + tm +
  geom_bar(aes(x = meta_analysis_self_described,
               fill = meta_analysis_weighted,
               y = ..count../sum(..count..)), width = 0.5,
           colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
  scale_fill_viridis_d() +
  labs(x = "Meta-analysis?",
       y = "Proportion",
       fill = "Weighted?") 
```

@@

```{r}
dat %>% mutate(cont_moderator_variable_modelled = if_else(cont_moderator_variable_modelled == "", "N/A", cont_moderator_variable_modelled)) %>% 
  ggplot() + tm +
  geom_bar(aes(x = cont_moderator_variable,
               fill = cont_moderator_variable_modelled,
               y = ..count../sum(..count..)), width = 0.5,
           colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
  scale_fill_viridis_d() +
  labs(x = "Nuisance Heterogenity?",
       y = "Proportion",
       fill = "Modelled Nuisance\n Heterogenity?") 
```
